---
title: "Chpt 1 Data Viz"
author: "EOeller"
date: "Oct 2, 2020"
output: html_document
---
### This walkthrough was made following R for Data Science Chapter 1 
### Data Visualization using ggplot2

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

When referring to a specific function of a package, we use the syntax package::function().  
For example, ggplot2::ggplot() tells us we are using the ggplot function in the ggplot2 package

First we will use the **mpg** dataframe to answer the question: **do cars with big engines use more fuel than cars with small engines**?

```{r}
mpg
```

Here we can see **displ**, the car's engine size, and **hwy**, the car's fuel efficiency on the highway.  
We will plot **mpg** with **displ** on the x-axis and **hwy** on the y-axis.

```{r}
ggplot(data=mpg) +
  geom_point(mapping= aes(x= displ, y = hwy))
```

In the plot we see a negative relationship between engine size and fuel efficiency.  
Cars with larger engines have lower fuel efficiency, meaning **cars with larger engines use more fuel**.

The first argument of ggplot() is the dataset you use to make the graph. Here it is **ggplot(data= mpg)**.
The next function geom_point() adds a layer of points to the plot, which creates a scatterplot.  
Each geom function takes a mapping() argument, which is always paired with a aes(x= , y= ).

Here is a template for making graphs in ggplot2.  
Replace DATA with your data, and MAPPING with your desired mapping.  

ggplot(data= DATA) +  
  GEOM_FUNCTION(mapping= aes(MAPPINGS))
  
